---
title: "Create Qld and NSW State Map Base"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r libraries}
library(rnaturalearth)
library(sf)
```

# Get the Data to Create Our Map

### Add a Shapefile of Australia

This is our base layer, Australia, of the map from [Naturalearth.com](https://naturalearth.com/).

```{r, australia}

oz <- ne_states(geounit = "australia", returnclass = "sf")

plot(oz)
```

## Crop and Reproject

However, for the data that this package is intended for use with, only New South Wales and
Queensland are necessary. 

Also for cartography purposes, we will reproject the map to Australian Albers for A.C.T., N.S.W and Qld.

Two objects are created, one `oz_label` for state outlines and labels and the other, `oz_outline` for a basic country outline to use over the top of `oz_label`.

```{r crop_shape}
bound <- raster::extent(131,
                        155,
                        -39,
                        -10)

oz_label <- sf::st_intersection(oz,
                             sf::st_set_crs(
                               sf::st_as_sf(
                                 as(bound,
                                    "SpatialPolygons")),
                               sf::st_crs(oz))) %>%
  sf::st_transform(crs = 3577)

oz_label <-
  oz_label %>%
  dplyr::mutate(
    CENTROID = purrr::map(geometry, sf::st_centroid),
    COORDS = purrr::map(CENTROID, sf::st_coordinates),
    COORDS_X = purrr::map_dbl(COORDS, 1),
    COORDS_Y = purrr::map_dbl(COORDS, 2)
  )

oz_label$nudge_x <- 0
oz_label$nudge_y <- 0

oz_outline <-
  oz %>%
  dplyr::group_by(admin) %>%
  dplyr::summarize() %>%
  sf::st_intersection(
    sf::st_set_crs(
      sf::st_as_sf(
        as(bound,
           "SpatialPolygons")),
      sf::st_crs(oz))) %>%
  sf::st_transform(crs = 3577)

plot(oz_label)

plot(oz_outline)
```

## Save Data for Use as Base Map

```{r save-data}
usethis::use_data(oz_label, overwrite = TRUE)
usethis::use_data(oz_outline, overwrite = TRUE)
```

## R System Information

```{r packages-used}
sessioninfo::session_info()
```